Wikipedia Text Mining and Surprisal Analysis

### 2019-07-16 surprisal/wiki_surprisal.Rmd
iso codes matched up

```{r get features, eval=T}
wkpd <- read.csv(here("Data/wikipedia_unigrams.csv"))
LANGUAGES <- wkpd$language

FEATURES <- c(1:144)
for (i in c(1:length(FEATURES))) {
  FEATURES[i] <- paste(FEATURES[i], "A", sep = "")
} #get all word order WALS features in correct syntax

@@

wiki_isos <- read_csv(here("Wikipedia/wiki_isos.csv")) %>%
  clean_names() %>%
  select(x639_1, x639_3)

wiki_langs <- fromJSON(here("/Wikipedia/language_dict.json")) %>%
  as_tibble() %>%
  gather(language, x639_1) %>%
  left_join(wiki_isos)

%>%
  left_join(wals_isos) %>%
  filter(is.na(wals.code)) %>%
  View()

wf <- wals.feature(FEATURES)

write_csv(wf, here("Data/wals.csv"))
```

@@

>>>>

```{r get features, eval=T}
wiki <- read_csv(here("Data/relative_ngrams.csv"))
LANGUAGES <- wiki %>% pull(language) %>% unique()

codes <- read_csv(here("Wikipedia/isos.csv"))

wals <- read_csv(here("Data/wals.csv"))

@@

wals_isos %>% 
  inner_join(codes, by = "iso") %>% 
  select(-language.x) %>%
  rename(language = language.y) %>% 
  inner_join(wiki %>% inner_join(codes, by = "language"), by = "iso")
```

@@

```{r setup}
wiki_isos <- read_csv(here("Wikipedia/wiki_isos.csv")) %>%
  clean_names() %>%
  select(iso_language_name, x639_1, x639_3) %>% 
  mutate(x639_3 = str_extract(x639_3, "\\w+")) %>% 
  rename(language = iso_language_name) %>% 
  filter(language %in% LANGUAGES)

wiki_langs <- fromJSON(here("Wikipedia/language_dict.json")) %>%
  as_tibble() %>%
  gather(language, x639_1) %>%
  filter(language %in% LANGUAGES) %>%
  left_join(wiki_isos)

%>%
  left_join(wals_isos) %>%
  filter(is.na(wals.code))
```
